Using traffic analysis to identify The Second Generation Onion Router

### 2011-02-26 thesis/experiment.tex
Remove script copied verbatim, refer to file instead

\begin{lstlisting}[language=ruby]
require "rubygems"
gem "rspec"
gem "selenium-client"
require "selenium/client"
require "selenium/rspec/spec_helper"

describe "site1.static.torsim.1" do
  attr_reader :selenium_driver
  alias :page :selenium_driver

  before(:all) do
    @verification_errors = []
    @selenium_driver = Selenium::Client::Driver.new \
      :host => "localhost",
      :port => 4444,
      :browser => "*firefoxproxy",
      :url => "https://site1.static.torsim/",
      :timeout_in_second => 60
  end

  before(:each) do
    @selenium_driver.start_new_browser_session
  end

  append_after(:each) do
    @selenium_driver.close_current_browser_session
    @verification_errors.should == []
  end

  it "test_site1.static.torsim.1" do
    page.open "/"
  end
end
\end{lstlisting}

@@

The Tor Network Guest is responsible for emulating a Tor network. It runs three
Tor directory authorities as well as fifteen relays. Tor was installed on the
Tor Network Guest using the same procedure listed in \ref{install-tor}. By
default the Tor installation runs at start time, but this is disabled by
removing execute permissions from the file \verb+/etc/init.d/tor+.

>>>>

\lstinputlisting[language=ruby]{../experiment/simulation/client/scripts/site1.static.torsim.1_spec.rb}

@@

The Tor Network Guest is responsible for emulating a Tor network. It runs three
Tor directory authorities as well as fifteen relays. Tor was installed on the
Tor Network Guest using the same procedure listed in \ref{install-tor}. By
default the Tor installation runs at start time, but this is disabled by
removing executable permissions from the file \verb+/etc/init.d/tor+.
